---
title: "Lab 00 - Hello IDS!"
author: "Adam Celecky"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Adam", "Jamie", "Dylan", 
           "Ben", "Yara", "Gandom"),
  github_username = c("adcel27", "jamieewen", "dylanhobman", 
                      "ben-251", "yarakanaann", "Gand0m"), 
  colour = c("green", "red", "blue", 
             "yellow", "peachpuff", "hotpink"),
  hobby = c("skiing", "football", "football", 
            "basketball", "badminton", "voleyball"),
  favourite_number = c(3, 9, 6, 4, 7, 8)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


The bar graph displays our favorite number in our favorite colour assigned to our username.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "username", 
          y = "favourite_number",
          title = "favourite_numbers")
```

The function labs () assigns labels to the graph.

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

There will be a very wide range of possible hobbies, so it will be probably more useful to show every hobby that doesn't reach certain count reassigned as other.
